---
title: "First `xaringan` presentation"
subtitle: "easy peasy"
author: "Katie Masiello"
date: "8/20/2020"
output: xaringan::moon_reader
customer: RStudio
---
```{r setup, include=FALSE}
library(palmerpenguins)
```

class: right
Hello I'm slide 1
# what happens here? 
class: left 
can I move to left?

---
name: slide2
And I'm slide 2
[go to that other slide](#protip)
---

# Header

And now I'll **spice it up**
---
# About *me*
I like cookies


---
class: center, middle, inverse 
each slide has its own YAML
choices for class:
* top
* bottom
* middle  
<br>
* left
* right 
* center  
<br>
* inverse



---
name: protip
## Pro Tip 
`remark.js`
[go to that other slide](#slide2)
---
# Guess what?  I love this font
---
# Incremental reveals
This is my first point  
--
wait for it...  
--
it's really cool  
--
I love _chocolate chip cookies_
---
# Let's do two columns
.pull-left[
Here's some text
]
.pull-right[
# Here's more text
]

---
# Let's do two columns
.left-column[
Here's some text that's in a narrower column
]
.right-column[
# Here's more text
With more room 
* and bullets
* and more
]

---
# Data
```{r}
summary(penguins)
```

---
Alison's YAML
```
author: Alison
date: '`r format(Sys.Date())`'
title: Presenting the penguins
output:
  xaringan::moon_reader:
    css:
    - default
    - rladies
    - rladies-fonts
    nature:
      highlightStyle: github
      highlightLines: true
      ```
      
---
# Side by side code + plot
Use clever chunk options to reference each chunk

1. Code first, plot second  
  * Chunk 1: {r plot-last, fig.show = 'hide'} #hide figure
  * Chunk 2: {r ref.label = 'plot-last', echo = FALSE} #dont show code
  

2. Plot first, code second
  * Chunk 1: {r plot-first, echo = FALSE}
  * Chunk 2: {r ref.label = 'plot-first', eval = FALSE}

---
# example of 1
.pull-left[
```{r plot-last, fig.show = 'hide'}
#code goes here
```
]
.pull-right[
```{r ref.label = 'plot-last', echo = FALSE}

```
]

---
example of 2 
.pull-left[
```{r plot-first, echo = FALSE}
#code goes here
```
]
.pull-right[
```{r ref.label = 'plot-first', eval = FALSE}
```
]
---
# Make a your turn index counter
```{r, include=FALSE}
yt <- 0
```
This is a hot tip to ensure you don't have to renumber and increment things wrong 
# Your turn # `r (yt <- yt + 1)`

Try this!

# Your turn # `r (yt <- yt + 1)`

Check this!

---
# Pull info from your YAML
could use this to customize customer presentations easily
Hi my name is `r rmarkdown::metadata$author` , and welcome to `r rmarkdown::metadata$title` for `r rmarkdown::metadata$customer`
---
# Use `params` to wrangle links
Maybe actually this would be a better place to put the customer name. 
```
params:
  wifi_name: TBD
  wifi_pass: penguins-are-the-new-iris
  cloud_link: RStudio Cloud link here
  repo_link: Link to Github here
  site_link: rstd.io/tip
  ```
  
